% TODO: 
% - Background on ADLs
% - Background on coking
% - Background on trying to assess cooking
% - Market analysis on cooking stuff
% - Background on technologies used to track cooking
% - Background on remote monitoring
%


\section{Overview}
In 2014, over 6 million Canadians (15.6\% of the population) were 65 years old or older. The number of older adults (65+) continues to increase; and by 2030, Statistics Canada expects there to be over 9.5 million adults over the age of 65, comprising 23\% of Canadians \cite{government_of_canada_daily_2014}. Frequently, older adults who wish to age-in-place or in the comfort of their own home must be able to perform their activities of daily living (ADLs) while bearing multiple diseases and syndromes that come with age, such as frailty, impaired cognition, gait and balance problems \cite{tijsen_challenging_2019}. These ADLs may include cooking, bathing, getting into and out of bed, and toileting all of which require complex coordination of the older adult’s cognitive, physical, visual, and perceptual abilities. Deficits in any of the categories mentioned can impair the older adult’s ability to go about their day. Typically it is only after an incident or hospitalization that an older adult is assessed for their ability to perform ADLs \cite{wilkinson_comprehensive_2021}. 

The current system presents an opportunity for proactive and preventative medicine through the use of in-home monitoring. Data obtained through monitoring can be used to track functional decline.With ths information, older adults, along with their clinician, can plan early interventions and prevent future incidents and hospitalization. The rest of the chapter will be organized as follows: first, an overview of the common diseases and conditions from aging that affect ADLs will be explored; next, current assessment tools for these conditions will discussed; finally, current attempts at in-home monitoring for ADLs will be investigated as well as what data and how the data is being used.

\section{Background for Diseases and Conditions in Aging}

This section reviews the current literature on the disease and conditions associated with aging. In terms of functionally being able to perform one's ADLs, both physical and cognitive ability are required. % TODO: read the tijsen_challenging_2019 articleand write about the diseases


There is an abundance of assessments that may be used to pinpoint problems with the patient’s ADLs. One of these assessments is the Performance Assessment of Self-Care Skills (PASS) where patients are asked to perform select activities and are assessed by their healthcare provider on their ability to perform each task. 

% TODO: Put in more of the assessments here

PASS assesses an individual’s ability to perform ADLs by judging 3 parameters: independence, safety and adequacy. There are concrete guidelines and identifiers mentioned for scoring each parameter in Performance Assessment of Self-Care Skills \cite{rogers_performance_2014}. For instance, the safety category has a maximum score of 3. At a score of 3, there are no risks observed; at a score of 2, there are minor risks observed, but no assistance is needed; at a score of 1, there are obvious risks to safety and assistance is required to complete a task; Finally, at a score of 0, there are risks to safety of such severity that the task had to be stopped. PASS is used around the world; has been translated to multiple languages including Spanish, Hebrew and Mandarin; has a test-retest reliability of 89\%-90\%; and an inter-observer agreement of 96\%-97\% \cite{chisholm_evaluating_2014} making it a reliable tool for assessing ADLs. 


Of the ADLs that PASS assesses, cooking was identified to be critical in terms of sustaining a healthy lifestyle in older adults \cite{bouchard_smart_2020} but fraught with risks \cite{yared_cooking_2015}. Older adults also cook frequently, with 53\% of older adults ages 65-80 reported to cook at home 6-7 days a week \cite{malani_joy_2020}. Despite the health benefits and enjoyment gained from cooking, cooking is a dangerous ADL and older adults with comorbidities may have difficulty cooking safely (older adults with cognitive impairments may forget about a stovetop or oven that is on, improper knife use can result in injury and unsafe kitchen environments may exacerbate injury from falls or increase the risk of falls); the kitchen is in second place for the location of most domestic accidents \cite{yared_cooking_2015}.PASS assesses the independence, safety and adequacy of the cooking ADL by splitting the cooking task into categories of oven use, stovetop use, use of sharp utensils, and cleanup after meal preparation each with a list of its own subtasks \cite{rogers_performance_2014}. The concrete classification framework provided by PASS allows for Smart Home (SH) interventions through monitoring and assessment with internet of things (IoT) devices.

Devices that have been used in literature cover a wide range of sensors. Logan and Healy used a modified form of AdaBoost with simple linear weak learners to distinguish meal preparation and eating through accelerometer, video capture, and audio capture data \cite{logan_sensors_2006}. Sarma et al. used Long short-term memory (LSTM) to determine various ADLs from datasets containing motion sensors, door closure sensors and temperature sensors data \cite{sarma_activity_2019}. Chibaudel et al. detected cooking by noting the physical location of the participant and their refrigerator usage through door sensors placed in the refrigerator and motion sensors in the kitchen \cite{mokhtari_smart_2018}. Yordanova et al. used Decision Trees (DT), Computational Causal Behavior Models (CCBM), and Hidden Markov Models (HMM) to process data from the full-scale SPHERE Smart Home system consisting of temperature sensors, humidity sensors, luminosity and motion sensors, water and electricity usage sensors, cameras, and door contact sensors to classify the preparation of a wide range of recipes as "cooking" \cite{yordanova_analysing_2019}.

Although there have been many studies involving the detection of the cooking ADL, few studies assess the quality of cooking and provide feedback to the user. The closest attempts at assessing quality involve quantifying the number of departures from a given task. Cook and Schmitter-Edgecombe used motion sensors, analog sensors for water and stove usage, open/shut sensors for the status of cabinets, and load sensors for the absent/present status of items to assess the quality of ADLs including meal preparation. If a correct sequence of tasks was done and if the task was done efficiently, then an activity is considered as normal. Any significant departures from this "correct sequence" and normal time required to complete each step was only left with a tag of "anomalous" \cite{cook_assessing_2009}. There is no further information with respect to how much of an anomaly the error was or what to do about it.  Similarly, in Menghi et al.'s study, errors were identified in a series of tasks, but nothing was done to evaluate the severity of the error and no feedback was given to the user \cite{mokhtari_smart_2018}. There is no impact on the user because errors were only identified. The user does not receive feedback about what areas need improvement and how to improve, because there was no evaluation using standardized assessments such as PASS.

The literature cites using AI techniques on data collected from IoT devices, from which two issues arise: a huge amount of data will be necessary to produce reliable classification models \cite{sarker_machine_2021}; and, to facilitate collection of these large datasets, data from various IoT device vendors must be easily extractable. To solve these two issues, this project will be part of a recent joint initiative between several Universities across Canada gave rise to the Program to Accelerate Technologies for Homecare (PATH) which will unify SH devices and their various communication protocols (including Bluetooth, Zigbee, and Wi-fi) into a plug-and-play cloud-based system. As the platform matures, PATH will collect data from both home-like labs and at least 350 homes across Canada by partnering with companies in the SH industry. Collecting from this many sources will lead to a huge database of real-world data that will be used to develop and improve AI algorithms for use in monitoring and detection of abnormalities present in the home or the user \cite{noauthor_path_nodate}.

The potential to rapidly collect data on various cooking scenarios provided from PATH, along with concrete classifiable items assessing the quality of cooking provided by the PASS framework can be used to create a novel and robust cooking quality assessment SH system that doubles as a tool for ensuring the safety of older adults in the kitchen and automation of cooking functional assessments for clinicians.

Objective and Methodology: The research project proposes the development of a cooking-focused SH monitoring system on the PATH platform for older adults to ensure that cooking is done safely and to automate cooking assessments for clinicians. This will involve selecting and testing commercially available devices to testing the entire system on patients at the Independent Living Suite (ILS) in the Glenrose Rehabilitation Hospital (GRH). To create a system that is easy to use for older adults and clinicians, they will be consulted at every step in the process. The research project can be broken down into 5 phases:

1.     Research the usability and acceptability of SH devices among older adults with a focus on how the usability and acceptability may be affected by the design of the devices. A UTAUT2 focus group study involving older adults (65+), care providers and clinicians will be conducted to obtain feedback for usability and acceptability;

2.     Research common data analytic tools and frameworks that are relevant for monitoring cooking through the PASS’s criteria. Keywords from the sub tasks outlined in PASS + “Machine Learning, Detection, Assessment” will be searched on the academic databases Scopus, PubMed, Cinahl, IEEE Explore, ISI Web of Sciences, and ACM Digital Library; and on the general web on StackOverflow, TowardsDataScience and TowardsAI;

3.     Select and validate commercially available SH devices tailored to the preferences from the usability study and clinical relevance from the literature review. This step involves searching for previous validation of the devices on Scopus, PubMed, Cinahl, IEEE Explore, ISI Web of Sciences, and ACM Digital Library along with any necessary validation of the devices in-lab by comparing to gold standards such as ECG for Heart Rate;

4.     Apply data analytics methodologies from the literature review to devices selected to assess cooking safety and function. The bulk of these algorithms will be written in Python and any other additional languages deemed necessary from the literature review will be used;

5.     Conduct a clinical pilot-study at the ILS with real-world participants to determine the sensitivity and specificity of devices when detecting the cooking activity and evaluate if users are cooking safely. The developed system will be installed into one living suite at the ILS and a single user will be monitored for the remaining duration of research project. Key outcomes investigated throughout the pilot-study involve cooking ADL detection F-score, cooking safety evaluation compared to clinicians’ judgement and effectiveness of automated SH interventions by comparing independence, safety and adequacy scores before and after.

 

The outcomes of this research project are four-fold: the development of a SH cooking safety system, an automated cooking assessment tool for clinicians, testing and further development of the PATH system, and contribution of data to the PATH system for other researchers.
